Sexual selection improves population fitness: a meta-analysis

### 2018-10-02 meta_analysis_sexual_selection_pop_fitness.Rmd
Fixed Blind Plot weights

```{r, fig.height= 6, fig.width=8}
blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
  geom_jitter(aes(fill=Blinding, size = 1/var.g), shape=21, color='grey20')+
  geom_boxplot(outlier.shape = NA, fill = NA)+
  geom_hline(yintercept=0, linetype = 'dotted') + 
  scale_fill_brewer(palette = "Set2")+
  labs(y="Effect size (Hedges' g)", x= 'Blinding', size = 'Weight (%)')+
  guides(fill=FALSE, size = guide_legend(override.aes = list(fill = "#66c2a5")))+
  theme_bw()+
  theme(panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(),
        text = element_text(size=14),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size=12),
        legend.title=element_text(size=12, face = "bold"),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))

>>>>

```{r, fig.height= 6, fig.width=8}
blind.plot <- df.forest.model %>% ggplot(aes(x=Blinding, y=g))+
  geom_jitter(aes(fill=Blinding, size = ((1/var.g)/27708.14)*100), shape=21, color='grey20')+ #total 1/var.g
  geom_boxplot(outlier.shape = NA, fill = NA)+
  geom_hline(yintercept=0, linetype = 'dotted') + 
  scale_fill_brewer(palette = "Set2")+
  labs(y="Effect size (Hedges' g)", x= 'Blinding', size = 'Weight (%)')+
  guides(fill=FALSE, size = guide_legend(override.aes = list(fill = "#66c2a5")))+
  theme_bw()+
  theme(panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(),
        text = element_text(size=14),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size=12),
        legend.title=element_text(size=12, face = "bold"),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))
